---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```

# tidyenigh

<!-- badges: start -->
[![R-CMD-check](https://github.com/estebandegetau/tidyenigh/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/estebandegetau/tidyenigh/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

Ships analysis-ready data from the Encuesta Nacional de Ingresos y Gastos de los Hogares [ENIGH](https://www.inegi.org.mx/programas/enigh/nc/2022/) survey to the user.

## Usage

Data is Lazy Loaded, so you can use it as soon as you load the package.
```{r}
library(tidyenigh)

poblacion_2022$lenguaind |> 
  summary() |> 
  head(10)
  
```

Data includes variable and value labels
```{r}
library(labelled)

gastoshogar_2022 |> 
  generate_dictionary(details = F) |> 
  head(10)

```

Official [INEGI](https://www.inegi.org.mx/) documentation is available within the package
```{r, eval=FALSE}
?hogares_2022
```

Check available data sets
```{r}
enigh_documentation_2022
```

## Installation

You can install the development version of `tidyenigh` from [GitHub](https://github.com/) with:

``` {r, eval = FALSE}
# install.packages("devtools")

devtools::install_github("estebandegetau/tidyenigh")
```


